Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-11 mtjournal.tex
footnote on deltas

To avoid this conflation, on the HTER corpora we report correlations
on $\bar{\mu}(m)$
and $\bar{\mu}(\textrm{HTER})$ (rather than measure $m$ and HTER), where
$\bar{\mu}$ represents mean-removal:
\begin{equation}
  \label{eq:meansub}
  \bar{\mu}(m(t_i)) = m(t_i) - \sum_{j=1}^I\frac{m(t_j)}{I}
\end{equation}
Mean-removal lowers the correlation $r$ values reported but ensures
that the reported correlations are among differences in the
translations rather than among differences in the underlying segments.

Section~\ref{sec:hter2} reports HTER correlations per-sentence. There,
we use length-weighted correlation, since unweighted correlations
effectively puts too much emphasis on short sentences.  We do not
weight for length in section~\ref{sec:hter1}, which reports document
correlations, because documents are assumed to be equally important
(regardless of length).

TO DO: MENTION DELTAS IN A FOOTNOTE, AND CITE MetricsMATR SYSTEM PAPER

>>>>

To avoid this conflation, on the HTER corpora we report correlations
on $\bar{\mu}(m)$
and $\bar{\mu}(\textrm{HTER})$ (rather than measure $m$ and HTER), where
$\bar{\mu}$ represents mean-removal:
\begin{equation}
  \label{eq:meansub}
  \bar{\mu}(m(t_i)) = m(t_i) - \sum_{j=1}^I\frac{m(t_j)}{I}
\end{equation}
Mean-removal lowers the correlation $r$ values reported but ensures
that the reported correlations are among differences in the
translations rather than among differences in the underlying segments.
\footnote{ Previous work \cite{kahn08metricsmatr} reported HTER
  correlations against pairwise differences among translation segments
  derived from the same source segment. Those results are similar to
  those reported here. However, we believe that pairwise differences
  introduce problems with the independence assumptions in
  the Pearson's $r$ tests, and we use mean-removal
  throughout this work instead.}

When reporting HTER correlations per-sentence, we use length-weighted
correlation, since unweighted correlations effectively puts too much
emphasis on short sentences.  We do not weight for length for the
per-document correlations in section~\ref{sec:hter1}, because we
assume documents to be equally important (regardless of length).
